spatial_figures

### 2025-03-29 spatial_figs.Rmd
updated precip fig to only include summer

```{r}
grid <- read_csv("/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/grid_all_Catchment.csv",
                 skip=3) %>%
   slice(3:n()) %>%
  dplyr::select(-starts_with('@'),
                -1) %>%
  mutate(date = ymd(time)) %>%
  dplyr::select(-time) %>%
  mutate_if(is.character, as.numeric) %>% 
  mutate(site = 'grid')

catchment_mo_mean <- all %>%
  mutate(month = month(date)) %>%
  group_by(site, month) %>%
  summarise(across(precip:solRad, ~ mean(.x, na.rm = TRUE))) %>%
  dplyr::select(site, month,
                precip_mean = precip, tmean_mean = tmean, 
                solrad_mean = solRad, rh_mean = rhum)

catchment_mo_sd <- all %>%
  mutate(month = month(date)) %>%
  group_by(site, month) %>%
  summarise(across(precip:solRad, ~ sd(.x, na.rm = TRUE))) %>%
  dplyr::select(site, month,
                precip_sd = precip, tmean_sd = tmean, 
                solrad_sd = solRad, rh_sd = rhum)

p_cols <- ggplot(catchment_mo2, aes(x = month_name, y = precip_mean,
                                    color = site, fill = site)) +
  geom_col(position = 'dodge') +
  geom_errorbar(aes(ymin = 0, ymax = precip_mean + precip_sd), 
                position = position_dodge(width = 0.6), width = 0.2) +
  scale_color_manual(values = c("blue", "orange"),
                     labels = c("Gridded", "Observed")) +  # Rename color legend items
  scale_fill_manual(values = c("blue", "orange"),
                    labels = c("Gridded", "Observed")) +   # Rename fill legend items
  theme_bw(base_size = 20) +
  labs(y = 'Precipitation (mm)',
       x = element_blank()) +
  guides(color = guide_legend(title = NULL),
         fill = guide_legend(title = NULL)) +
    theme(
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    strip.text = element_blank()
  )

ggsave("P.png", plot = p_cols, width = 8, height = 6, dpi = 300)

# Temperature plot
t_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = tmean_mean, 
                                      color = site, group = site)) +
  geom_ribbon(aes(ymin = tmean_mean - tmean_sd, ymax = tmean_mean + tmean_sd, fill = site), alpha = 0.2) +
  geom_line() +
  geom_point() +
  scale_color_manual(values = c("blue", "orange"),
                     labels = c("Gridded", "Observed")) +  # Set line color to blue and orange and rename
  scale_fill_manual(values = c("blue", "orange"),
                    labels = c("Gridded", "Observed")) +   # Set ribbon fill color to blue and orange and rename
  theme_bw(base_size=12) +
  labs(y = expression("Mean temperature " ( degree~C)),
       x = element_blank()) +
  labs(color = NULL, fill = NULL)

# Solar radiation plot
sol_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = solrad_mean, 
                                         color = site, group = site)) +
  geom_ribbon(aes(ymin = solrad_mean - solrad_sd, ymax = solrad_mean + solrad_sd, fill = site), alpha = 0.2) +
  geom_line() +
  geom_point() +
  scale_color_manual(values = c("blue", "orange"),
                     labels = c("Gridded", "Observed")) +  # Set line color to blue and orange and rename
  scale_fill_manual(values = c("blue", "orange"),
                    labels = c("Gridded", "Observed")) +   # Set ribbon fill color to blue and orange and rename
  theme_bw(base_size = 12) +
  labs(y = expression("Solar radiation (MJ/m"^"2" * ")"),
       x = element_blank()) +
  labs(color = NULL, fill = NULL)

# Relative humidity plot
rh_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = rh_mean, 
                                        color = site, group = site)) +
  geom_ribbon(aes(ymin = rh_mean - rh_sd, ymax = rh_mean + rh_sd, fill = site), alpha = 0.2) +
  geom_line() +
  geom_point() +
  scale_color_manual(values = c("blue", "orange"),
                     labels = c("Gridded", "Observed")) +  # Set line color to blue and orange and rename
  scale_fill_manual(values = c("blue", "orange"),
                    labels = c("Gridded", "Observed")) +   # Set ribbon fill color to blue and orange and rename
  theme_bw(base_size = 12) +
  labs(y = 'RH (%)', x= element_blank()) +
  labs(color = NULL, fill = NULL)

# Print the plots
t_moplot
sol_moplot
rh_moplot

# t_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = tmean_mean, 
#                                       color = site, group = site)) +
#   geom_ribbon(aes(ymin = tmean_mean - tmean_sd, ymax = tmean_mean + tmean_sd, fill = site), alpha = 0.2) +
#   geom_line() +
#   geom_point() +
#   theme_bw(base_size=14) +
#   labs(y = expression("Mean temperature " ( degree~C)),
#        x = element_blank())
# 
# t_moplot
# 
# sol_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = solrad_mean, 
#                                       color = site, group = site)) +
#   geom_ribbon(aes(ymin = solrad_mean - solrad_sd, ymax = solrad_mean + solrad_sd, fill = site), alpha = 0.2) +
#   geom_line() +
#   geom_point() +
#   theme_bw(base_size = 14) +
#   labs(y = expression("Solar radiation (MJ/m"^"2" * ")"),
#        x = element_blank()) 
# 
# sol_moplot
# 
# 
# rh_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = rh_mean, 
#                                       color = site, group = site)) +
#   geom_ribbon(aes(ymin = rh_mean - rh_sd, ymax = rh_mean + rh_sd, fill = site), alpha = 0.2) +
#   geom_line() +
#   geom_point() +
#   theme_bw(base_size = 14) +
#   labs(y = 'RH (%)', x= element_blank()) 
# rh_moplot
library(ggpubr)

ggsave("./figures/quad.png", plot = quad, dpi = 600)

quad_plus <- ggarrange(flow_plot,quad,
                       nrow=2)
quad_plus

ggsave("./figures/quad_plus.png", plot = quad_plus, dpi = 600)

# difference - UPDATE file sources!!

@@

#grid first
setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/HRU_output/grid")

read_ages_grid <- function(dataframe){
  read_csv(dataframe, skip = 3) %>%
  slice(3:n()) %>%
  dplyr::select(-starts_with('@'),
                -1) %>%
  mutate(time = ymd(time)) %>%
  mutate_if(is.character, as.numeric) %>%
  mutate(source = 'grid')

}

#pull in all filenames with HRU in the name
filenames <- list.files(".", pattern="HRU", full.names=F)

#read all the csvs using read_ages function
dataframes <- lapply(filenames, read_ages_grid)

#name all the csvs based on first 6 characters
names(dataframes) <- substr(filenames, 1, 6)

#bind all and make 1 df
hru_grids <- dataframes %>%
  bind_rows()

#statn next
setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/HRU_output/statn")

read_ages_statn <- function(dataframe){
  read_csv(dataframe, skip = 3) %>%
  slice(3:n()) %>%
  dplyr::select(-starts_with('@'),
                -1) %>%
  mutate(time = ymd(time)) %>%
  mutate_if(is.character, as.numeric) %>%
  mutate(source = 'statn')

}

#pull in all filenames with HRU in the name
filenames <- list.files(".", pattern="HRU", full.names=F)

#read all the csvs using read_ages function
dataframes <- lapply(filenames, read_ages_statn)

#name all the csvs based on first 6 characters
names(dataframes) <- substr(filenames, 1, 6)

#bind all and make 1 df
hru_statn <- dataframes %>%
  bind_rows()

#get rid of a bunch of data
hru_grid_tmean <- hru_grids %>%
  dplyr::select(c(time, ID, tmean)) %>%
  rename(tmean_grid = tmean)  %>%
  group_by(ID) %>%
  summarize(tmean_all_grid = mean(tmean_grid))

hru_statn_tmean <- hru_statn %>%
  dplyr::select(c(time, ID, tmean)) %>%
  rename(tmean_statn = tmean) %>%
  group_by(ID) %>%
  summarize(tmean_all_statn = mean(tmean_statn))

tmean_hrus <- left_join(hru_grid_tmean, hru_statn_tmean, by = c('ID')) %>%
  mutate(diff = tmean_all_statn - tmean_all_grid) %>%
  rename(value = ID)

hrus_map_tmean <- left_join(hru_new, tmean_hrus, by = 'value')

# T max
#get rid of a bunch of data
hru_grid_tmax <- hru_grids %>%
  dplyr::select(c(time, ID, tmax)) %>%
  rename(tmax_grid = tmax)  %>%
  group_by(ID) %>%
  summarize(tmax_all_grid = mean(tmax_grid))

hru_statn_tmax <- hru_statn %>%
  dplyr::select(c(time, ID, tmax)) %>%
  rename(tmax_statn = tmax) %>%
  group_by(ID) %>%
  summarize(tmax_all_statn = mean(tmax_statn))

tmax_hrus <- left_join(hru_grid_tmax, hru_statn_tmax, by = c('ID')) %>%
  mutate(diff = tmax_all_statn - tmax_all_grid) %>%
  rename(value = ID)

hrus_map_tmax <- left_join(hru_new, tmax_hrus, by = 'value')

# Tmin
#get rid of a bunch of data
hru_grid_tmin <- hru_grids %>%
  dplyr::select(c(time, ID, tmin)) %>%
  rename(tmin_grid = tmin)  %>%
  group_by(ID) %>%
  summarize(tmin_all_grid = mean(tmin_grid))

hru_statn_tmin <- hru_statn %>%
  dplyr::select(c(time, ID, tmin)) %>%
  rename(tmin_statn = tmin) %>%
  group_by(ID) %>%
  summarize(tmin_all_statn = mean(tmin_statn))

tmin_hrus <- left_join(hru_grid_tmin, hru_statn_tmin, by = c('ID')) %>%
  mutate(diff = tmin_all_statn - tmin_all_grid) %>%
  rename(value = ID)

hrus_map_tmin <- left_join(hru_new, tmin_hrus, by = 'value')

setwd("~/Documents/Repos/fourmile")

# Cumulative p
hru_grid_precip <- hru_grids %>%
  dplyr::select(c(time, ID, precip)) %>%
  rename(precip_grid = precip)

hru_statn_precip <- hru_statn %>%
  dplyr::select(c(time, ID, precip)) %>%
  rename(precip_statn = precip)

precip_hrus <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>%
  mutate(diff = precip_statn - precip_grid,
         year = year(time)) %>%
  group_by(year, ID) %>%
  mutate(total_diff = cumsum(diff)) %>%
  filter(time == max(time)) %>%
  group_by(ID) %>%
  summarize(precip_avg_cumdiff = mean(total_diff)) %>%
  rename(value = ID)

hrus_map_precip <- left_join(hru_new, precip_hrus, by = 'value')

# solar rad
hru_grid_solrad <- hru_grids %>%
  dplyr::select(c(time, ID, solRad)) %>%
  rename(solrad_grid = solRad)  %>%
  group_by(ID) %>%
  summarize(solrad_all_grid = mean(solrad_grid))

hru_statn_solrad <- hru_statn %>%
  dplyr::select(c(time, ID, solRad)) %>%
  rename(solrad_statn = solRad) %>%
  group_by(ID) %>%
  summarize(solrad_all_statn = mean(solrad_statn))

solrad_hrus <- left_join(hru_grid_solrad, hru_statn_solrad, by = c('ID')) %>%
  mutate(diff = solrad_all_statn - solrad_all_grid) %>%
  rename(value = ID)

hrus_map_solrad <- left_join(hru_new, solrad_hrus, by = 'value')

# RH
#get rid of a bunch of data
hru_grid_rh <- hru_grids %>%
  dplyr::select(c(time, ID, rhum)) %>%
  rename(rh_grid = rhum)  %>%
  group_by(ID) %>%
  summarize(rh_all_grid = mean(rh_grid))

hru_statn_rh <- hru_statn %>%
  dplyr::select(c(time, ID, rhum)) %>%
  rename(rh_statn = rhum) %>%
  group_by(ID) %>%
  summarize(rh_all_statn = mean(rh_statn))

rh_hrus <- left_join(hru_grid_rh, hru_statn_rh, by = c('ID')) %>%
  mutate(diff = rh_all_statn - rh_all_grid) %>%
  rename(value = ID)

hrus_map_rh <- left_join(hru_new, rh_hrus, by = 'value')

####
rh <- ggplot() +
  geom_sf(data = hrus_map_rh, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "viridis", name = "RH (%)") +
  theme_bw(base_size=15.5) +
  theme_void() + bottom_theme

rh

sr <- ggplot() +
  geom_sf(data = hrus_map_solrad, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "cividis", name = expression("Srad (MJ/m"^"2" * ")")) +
  theme_bw(base_size=15.5) +
  theme_void() + top_theme

sr

precip <- ggplot() +
  geom_sf(data = hrus_map_precip, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "mako", name = "Cumulative P (mm)") +
  theme_bw(base_size=15.5) +
  theme_void() + top_theme

precip

tmean <- ggplot() +
  geom_sf(data = hrus_map_tmean, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "plasma", name = "Tmean (°C)",
                       limits = c(-5, 2)) +
  theme_bw(base_size=15.5) +
  theme_void() + bottom_theme

tmean

tmin <- ggplot() +
  geom_sf(data = hrus_map_tmin, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "plasma", name = "Tmin (°C)",
                       limits = c(-5, 2)) +
  theme_bw(base_size=15.5) +
  theme_void() + bottom_theme

tmin

tmax <- ggplot() +
  geom_sf(data = hrus_map_tmax, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "plasma", name = "Tmax (°C)",
                       limits = c(-5, 2)) +
  theme_bw(base_size=15.5) +
  theme_void() + bottom_theme

tmax

bottom_theme <-   theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    legend.key.width = unit(.75, "cm"),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    plot.margin = unit(c(-6, 0, 0, 0), "cm"), 
    panel.spacing = unit(0, "lines"))

top_theme <-   theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    legend.key.width = unit(.75, "cm"),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    plot.margin = unit(c(0, 0, -6, 0), "cm"), 
    panel.spacing = unit(0, "lines"))

lots <- ggarrange(
  precip, sr, rh, tmean,
  heights = 1)

lots

ggsave("./figures/diff_update2.png", plot = lots, dpi = 600)

# Pgrid vs Pstatn

statn_catch <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_model/output/4milecreek38HRUs-statnall_#1/out/Catchment.csv',
                        skip=3) %>%
  slice(3:n()) %>%
  dplyr::select(-starts_with('@'),
                -1) %>%
  mutate(time = ymd(time)) %>%
  mutate_if(is.character, as.numeric) %>%
  mutate(source = 'statn')

grid_catch <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_model/output/4milecreek38HRUs-gridall_#1/out/Catchment.csv',
                       skip=3) %>%
  slice(3:n()) %>%
  dplyr::select(-starts_with('@'),
                -1) %>%
  mutate(time = ymd(time)) %>%
  mutate_if(is.character, as.numeric) %>%
  mutate(source = 'grid')

catchment_p <- bind_rows(statn_catch, grid_catch) %>%
  dplyr::select(precip, time, source) %>%
  pivot_wider(., names_from=source, values_from=precip)

p_comp <- ggplot(catchment_p, aes(x=statn, y=grid)) + geom_point(size = 3) +
  theme_bw(base_size=25) +
  labs(x = 'Station precip (mm)',
       y = 'Grid precip (mm)') +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red")

p_comp
ggsave("./figures/p_compare.png", plot = p_comp, dpi = 600)

>>>>

@@

# grid <- read_csv("/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/grid_all_Catchment.csv",
#                  skip=3) %>%
#    slice(3:n()) %>%
#   dplyr::select(-starts_with('@'),
#                 -1) %>%
#   mutate(date = ymd(time)) %>%
#   dplyr::select(-time) %>%
#   mutate_if(is.character, as.numeric) %>% 
#   mutate(site = 'grid')
# 
# statn <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/statn_all_Catchment.csv',
#                  skip=3) %>%
#    slice(3:n()) %>%
#   dplyr::select(-starts_with('@'),
#                 -1) %>%
#   mutate(date = ymd(time)) %>%
#   dplyr::select(-time) %>%
#   mutate_if(is.character, as.numeric) %>% 
#   mutate(site = 'statn')
# 
# all <- bind_rows(grid, statn) %>%
#   arrange(date)
# 
# catchment_mo_mean <- all %>%
#   mutate(month = month(date)) %>%
#   group_by(site, month) %>%
#   summarise(across(precip:solRad, ~ mean(.x, na.rm = TRUE))) %>%
#   dplyr::select(site, month,
#                 precip_mean = precip, tmean_mean = tmean, 
#                 solrad_mean = solRad, rh_mean = rhum)
# 
# catchment_mo_sd <- all %>%
#   mutate(month = month(date)) %>%
#   group_by(site, month) %>%
#   summarise(across(precip:solRad, ~ sd(.x, na.rm = TRUE))) %>%
#   dplyr::select(site, month,
#                 precip_sd = precip, tmean_sd = tmean, 
#                 solrad_sd = solRad, rh_sd = rhum)
# 
# 
# catchment_mo <- left_join(catchment_mo_mean, catchment_mo_sd, 
#                           by = c('month', 'site'))
# 
# catchment_mo2 <- catchment_mo %>%
#   mutate(month_name = month.abb[month]) %>%
#   mutate(month_name = factor(month_name, 
#                              levels = c('Jan', 'Feb', 'Mar',
#                                         'Apr', 'May', 'Jun',
#                                         'Jul', 'Aug', 'Sep',
#                                         'Oct', 'Nov', 'Dec')))
# 
# 
# p_cols <- catchment_mo2 %>% 
#   filter(month_name %in% c('Jun','Jul','Aug', 'Sep')) %>%
#   ggplot(., aes(x = month_name, y = precip_mean,
#                                     color = site, fill = site)) +
#   geom_col(position = 'dodge') +
#   geom_errorbar(aes(ymin = 0, ymax = precip_mean + precip_sd), 
#                 position = position_dodge(width = 0.6), width = 0.2) +
#   scale_color_manual(values = c("blue", "orange"),
#                      labels = c("Gridded", "Observed")) +  # Rename color legend items
#   scale_fill_manual(values = c("blue", "orange"),
#                     labels = c("Gridded", "Observed")) +   # Rename fill legend items
#   theme_bw(base_size = 20) +
#   labs(y = 'Precipitation (mm)',
#        x = element_blank()) +
#   guides(color = guide_legend(title = NULL),
#          fill = guide_legend(title = NULL)) +
#     theme(
#     panel.grid = element_blank(),
#     panel.background = element_rect(fill = "white"),
#     text = element_text(color = "black"),
#     axis.title = element_text(color = "black"),
#     axis.text = element_text(color = "black"),
#     strip.text = element_blank()
#   ) 
# 
# 
# p_cols
# 
# ggsave("P.png", plot = p_cols, width = 8, height = 6, dpi = 300)
# 
# # Temperature plot
# t_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = tmean_mean, 
#                                       color = site, group = site)) +
#   geom_ribbon(aes(ymin = tmean_mean - tmean_sd, ymax = tmean_mean + tmean_sd, fill = site), alpha = 0.2) +
#   geom_line() +
#   geom_point() +
#   scale_color_manual(values = c("blue", "orange"),
#                      labels = c("Gridded", "Observed")) +  # Set line color to blue and orange and rename
#   scale_fill_manual(values = c("blue", "orange"),
#                     labels = c("Gridded", "Observed")) +   # Set ribbon fill color to blue and orange and rename
#   theme_bw(base_size=20) +
#   labs(y = expression("Mean temperature " ( degree~C)),
#        x = element_blank()) +
#    guides(color = guide_legend(title = NULL),
#          fill = guide_legend(title = NULL)) +
#     theme(
#     panel.grid = element_blank(),
#     panel.background = element_rect(fill = "white"),
#     text = element_text(color = "black"),
#     axis.title = element_text(color = "black"),
#     axis.text = element_text(color = "black"),
#     strip.text = element_blank()
#   ) 
# 
# # Solar radiation plot
# sol_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = solrad_mean, 
#                                          color = site, group = site)) +
#   geom_ribbon(aes(ymin = solrad_mean - solrad_sd, ymax = solrad_mean + solrad_sd, fill = site), alpha = 0.2) +
#   geom_line() +
#   geom_point() +
#   scale_color_manual(values = c("blue", "orange"),
#                      labels = c("Gridded", "Observed")) +  # Set line color to blue and orange and rename
#   scale_fill_manual(values = c("blue", "orange"),
#                     labels = c("Gridded", "Observed")) +   # Set ribbon fill color to blue and orange and rename
#   theme_bw(base_size = 20) +
#   labs(y = expression("Solar radiation (MJ/m"^"2" * ")"),
#        x = element_blank()) +
#    guides(color = guide_legend(title = NULL),
#          fill = guide_legend(title = NULL)) +
#     theme(
#     panel.grid = element_blank(),
#     panel.background = element_rect(fill = "white"),
#     text = element_text(color = "black"),
#     axis.title = element_text(color = "black"),
#     axis.text = element_text(color = "black"),
#     strip.text = element_blank()
#   ) 
# 
# # Relative humidity plot
# rh_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = rh_mean, 
#                                         color = site, group = site)) +
#   geom_ribbon(aes(ymin = rh_mean - rh_sd, ymax = rh_mean + rh_sd, fill = site), alpha = 0.2) +
#   geom_line() +
#   geom_point() +
#   scale_color_manual(values = c("blue", "orange"),
#                      labels = c("Gridded", "Observed")) +  # Set line color to blue and orange and rename
#   scale_fill_manual(values = c("blue", "orange"),
#                     labels = c("Gridded", "Observed")) +   # Set ribbon fill color to blue and orange and rename
#   theme_bw(base_size = 20) +
#   labs(y = 'RH (%)', x= element_blank()) +
#    guides(color = guide_legend(title = NULL),
#          fill = guide_legend(title = NULL)) +
#     theme(
#     panel.grid = element_blank(),
#     panel.background = element_rect(fill = "white"),
#     text = element_text(color = "black"),
#     axis.title = element_text(color = "black"),
#     axis.text = element_text(color = "black"),
#     strip.text = element_blank()
#   ) 
# 
# # Print the plots
# t_moplot
# sol_moplot
# rh_moplot
# 
# 
# # t_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = tmean_mean, 
# #                                       color = site, group = site)) +
# #   geom_ribbon(aes(ymin = tmean_mean - tmean_sd, ymax = tmean_mean + tmean_sd, fill = site), alpha = 0.2) +
# #   geom_line() +
# #   geom_point() +
# #   theme_bw(base_size=14) +
# #   labs(y = expression("Mean temperature " ( degree~C)),
# #        x = element_blank())
# # 
# # t_moplot
# # 
# # sol_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = solrad_mean, 
# #                                       color = site, group = site)) +
# #   geom_ribbon(aes(ymin = solrad_mean - solrad_sd, ymax = solrad_mean + solrad_sd, fill = site), alpha = 0.2) +
# #   geom_line() +
# #   geom_point() +
# #   theme_bw(base_size = 14) +
# #   labs(y = expression("Solar radiation (MJ/m"^"2" * ")"),
# #        x = element_blank()) 
# # 
# # sol_moplot
# # 
# # 
# # rh_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = rh_mean, 
# #                                       color = site, group = site)) +
# #   geom_ribbon(aes(ymin = rh_mean - rh_sd, ymax = rh_mean + rh_sd, fill = site), alpha = 0.2) +
# #   geom_line() +
# #   geom_point() +
# #   theme_bw(base_size = 14) +
# #   labs(y = 'RH (%)', x= element_blank()) 
# # rh_moplot
# library(ggpubr)
# 
# quad <- ggarrange(p_cols, 
#           t_moplot,
#           sol_moplot,
#           rh_moplot,
#           common.legend = T,
#           legend = 'bottom',
#           ncol=2,
#           nrow=2) 
#           #nrow = 4)
#           #ncol= 0)
# quad
# 
# ggsave("./figures/quad.png", plot = quad, dpi = 600)
# 
# quad_plus <- ggarrange(flow_plot2,quad,
#                        nrow=2)
# quad_plus
# 
# ggsave("/Users/megansears/Documents/Repos/fourmile/figures/quad_plus_20250329.png", plot = quad_plus, dpi = 600)
# 
# 
# ```
# 
# # difference - UPDATE file sources!!
# 
# ```{r}
# 
# #grid first
# setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/HRU_output/grid")
# 
# read_ages_grid <- function(dataframe){
#   read_csv(dataframe, skip = 3) %>%
#   slice(3:n()) %>%
#   dplyr::select(-starts_with('@'),
#                 -1) %>%
#   mutate(time = ymd(time)) %>%
#   mutate_if(is.character, as.numeric) %>%
#   mutate(source = 'grid')
# 
# }
# 
# #pull in all filenames with HRU in the name
# filenames <- list.files(".", pattern="HRU", full.names=F)
# 
# #read all the csvs using read_ages function
# dataframes <- lapply(filenames, read_ages_grid)
# 
# #name all the csvs based on first 6 characters
# names(dataframes) <- substr(filenames, 1, 6)
# 
# #bind all and make 1 df
# hru_grids <- dataframes %>%
#   bind_rows()
# 
# #statn next
# setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/HRU_output/statn")
# 
# read_ages_statn <- function(dataframe){
#   read_csv(dataframe, skip = 3) %>%
#   slice(3:n()) %>%
#   dplyr::select(-starts_with('@'),
#                 -1) %>%
#   mutate(time = ymd(time)) %>%
#   mutate_if(is.character, as.numeric) %>%
#   mutate(source = 'statn')
# 
# }
# 
# #pull in all filenames with HRU in the name
# filenames <- list.files(".", pattern="HRU", full.names=F)
# 
# #read all the csvs using read_ages function
# dataframes <- lapply(filenames, read_ages_statn)
# 
# #name all the csvs based on first 6 characters
# names(dataframes) <- substr(filenames, 1, 6)
# 
# #bind all and make 1 df
# hru_statn <- dataframes %>%
#   bind_rows()
# 
# #get rid of a bunch of data
# hru_grid_tmean <- hru_grids %>%
#   dplyr::select(c(time, ID, tmean)) %>%
#   rename(tmean_grid = tmean)  %>%
#   group_by(ID) %>%
#   summarize(tmean_all_grid = mean(tmean_grid))
# 
# hru_statn_tmean <- hru_statn %>%
#   dplyr::select(c(time, ID, tmean)) %>%
#   rename(tmean_statn = tmean) %>%
#   group_by(ID) %>%
#   summarize(tmean_all_statn = mean(tmean_statn))
# 
# tmean_hrus <- left_join(hru_grid_tmean, hru_statn_tmean, by = c('ID')) %>%
#   mutate(diff = tmean_all_statn - tmean_all_grid) %>%
#   rename(value = ID)
# 
# hrus_map_tmean <- left_join(hru_new, tmean_hrus, by = 'value')
# 
# # T max
# #get rid of a bunch of data
# hru_grid_tmax <- hru_grids %>%
#   dplyr::select(c(time, ID, tmax)) %>%
#   rename(tmax_grid = tmax)  %>%
#   group_by(ID) %>%
#   summarize(tmax_all_grid = mean(tmax_grid))
# 
# hru_statn_tmax <- hru_statn %>%
#   dplyr::select(c(time, ID, tmax)) %>%
#   rename(tmax_statn = tmax) %>%
#   group_by(ID) %>%
#   summarize(tmax_all_statn = mean(tmax_statn))
# 
# tmax_hrus <- left_join(hru_grid_tmax, hru_statn_tmax, by = c('ID')) %>%
#   mutate(diff = tmax_all_statn - tmax_all_grid) %>%
#   rename(value = ID)
# 
# hrus_map_tmax <- left_join(hru_new, tmax_hrus, by = 'value')
# 
# 
# # Tmin
# #get rid of a bunch of data
# hru_grid_tmin <- hru_grids %>%
#   dplyr::select(c(time, ID, tmin)) %>%
#   rename(tmin_grid = tmin)  %>%
#   group_by(ID) %>%
#   summarize(tmin_all_grid = mean(tmin_grid))
# 
# hru_statn_tmin <- hru_statn %>%
#   dplyr::select(c(time, ID, tmin)) %>%
#   rename(tmin_statn = tmin) %>%
#   group_by(ID) %>%
#   summarize(tmin_all_statn = mean(tmin_statn))
# 
# tmin_hrus <- left_join(hru_grid_tmin, hru_statn_tmin, by = c('ID')) %>%
#   mutate(diff = tmin_all_statn - tmin_all_grid) %>%
#   rename(value = ID)
# 
# hrus_map_tmin <- left_join(hru_new, tmin_hrus, by = 'value')
# 
# setwd("~/Documents/Repos/fourmile")
# 
# # Cumulative p
# hru_grid_precip <- hru_grids %>%
#   dplyr::select(c(time, ID, precip)) %>%
#   rename(precip_grid = precip)
# 
# hru_statn_precip <- hru_statn %>%
#   dplyr::select(c(time, ID, precip)) %>%
#   rename(precip_statn = precip)
# 
# precip_hrus <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>%
#   mutate(diff = precip_statn - precip_grid,
#          year = year(time)) %>%
#   group_by(year, ID) %>%
#   mutate(total_diff = cumsum(diff)) %>%
#   filter(time == max(time)) %>%
#   group_by(ID) %>%
#   summarize(precip_avg_cumdiff = mean(total_diff)) %>%
#   rename(value = ID)
# 
# hrus_map_precip <- left_join(hru_new, precip_hrus, by = 'value')
# 
# 
# # solar rad
# hru_grid_solrad <- hru_grids %>%
#   dplyr::select(c(time, ID, solRad)) %>%
#   rename(solrad_grid = solRad)  %>%
#   group_by(ID) %>%
#   summarize(solrad_all_grid = mean(solrad_grid))
# 
# hru_statn_solrad <- hru_statn %>%
#   dplyr::select(c(time, ID, solRad)) %>%
#   rename(solrad_statn = solRad) %>%
#   group_by(ID) %>%
#   summarize(solrad_all_statn = mean(solrad_statn))
# 
# solrad_hrus <- left_join(hru_grid_solrad, hru_statn_solrad, by = c('ID')) %>%
#   mutate(diff = solrad_all_statn - solrad_all_grid) %>%
#   rename(value = ID)
# 
# hrus_map_solrad <- left_join(hru_new, solrad_hrus, by = 'value')
# 
# 
# # RH
# #get rid of a bunch of data
# hru_grid_rh <- hru_grids %>%
#   dplyr::select(c(time, ID, rhum)) %>%
#   rename(rh_grid = rhum)  %>%
#   group_by(ID) %>%
#   summarize(rh_all_grid = mean(rh_grid))
# 
# hru_statn_rh <- hru_statn %>%
#   dplyr::select(c(time, ID, rhum)) %>%
#   rename(rh_statn = rhum) %>%
#   group_by(ID) %>%
#   summarize(rh_all_statn = mean(rh_statn))
# 
# rh_hrus <- left_join(hru_grid_rh, hru_statn_rh, by = c('ID')) %>%
#   mutate(diff = rh_all_statn - rh_all_grid) %>%
#   rename(value = ID)
# 
# hrus_map_rh <- left_join(hru_new, rh_hrus, by = 'value')
# 
# ####
# rh <- ggplot() +
#   geom_sf(data = hrus_map_rh, aes(fill = diff), color = "black", lwd = 0.2) +
#   scale_fill_viridis_c(option = "viridis", name = "RH (%)") +
#   theme_bw(base_size=15.5) +
#   theme_void() + bottom_theme
# 
# rh
# 
# sr <- ggplot() +
#   geom_sf(data = hrus_map_solrad, aes(fill = diff), color = "black", lwd = 0.2) +
#   scale_fill_viridis_c(option = "cividis", name = expression("Srad (MJ/m"^"2" * ")")) +
#   theme_bw(base_size=15.5) +
#   theme_void() + top_theme
# 
# 
# sr
# 
# precip <- ggplot() +
#   geom_sf(data = hrus_map_precip, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
#   scale_fill_viridis_c(option = "mako", name = "Cumulative P (mm)") +
#   theme_bw(base_size=15.5) +
#   theme_void() + top_theme
# 
# precip
# 
# tmean <- ggplot() +
#   geom_sf(data = hrus_map_tmean, aes(fill = diff), color = "black", lwd = 0.2) +
#   scale_fill_viridis_c(option = "plasma", name = "Tmean (°C)",
#                        limits = c(-5, 2)) +
#   theme_bw(base_size=15.5) +
#   theme_void() + bottom_theme
# 
# tmean
# 
# 
# tmin <- ggplot() +
#   geom_sf(data = hrus_map_tmin, aes(fill = diff), color = "black", lwd = 0.2) +
#   scale_fill_viridis_c(option = "plasma", name = "Tmin (°C)",
#                        limits = c(-5, 2)) +
#   theme_bw(base_size=15.5) +
#   theme_void() + bottom_theme
# 
# tmin
# 
# tmax <- ggplot() +
#   geom_sf(data = hrus_map_tmax, aes(fill = diff), color = "black", lwd = 0.2) +
#   scale_fill_viridis_c(option = "plasma", name = "Tmax (°C)",
#                        limits = c(-5, 2)) +
#   theme_bw(base_size=15.5) +
#   theme_void() + bottom_theme
#   
# tmax
# 
# bottom_theme <-   theme(
#     legend.position = "bottom",
#     panel.grid.major = element_blank(),
#     legend.key.width = unit(.75, "cm"),
#     panel.grid.minor = element_blank(),
#     axis.title.x = element_blank(),
#     axis.title.y = element_blank(),
#     plot.margin = unit(c(-6, 0, 0, 0), "cm"), 
#     panel.spacing = unit(0, "lines"))
# 
# top_theme <-   theme(
